Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-05 paper/Intuition.tex
Cleanup Refinement text a bit.

The store atomicity is a whole system property. Intuitively our
protocol is correct because it guarantees that at most one cache can
write at a time, and that any cache that attempts to read has
the ``latest'' value. We can state this formally with the following 4
invariants.

>>>>

Store atomicity is a whole system property. Intuitively our
protocol is correct because it guarantees at most one cache may
write at a time, and that any cache permitted to read has
the ``latest'' value. We state this formally with the following 4
invariants.
